%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Ethan Brockmann}{}

\address{740 Hartwood, Brandon, MS 39042}

\mobile{(920) 728-5600}
\email{\href{mailto:ethanbrockmann@gmail.com}{\nolinkurl{ethanbrockmann@gmail.com}}}
\github{EeethB}
\community{EeethB}
\angellist{ethan-brockmann}
\linkedin{ethan-brockmann}
\twitter{EeethB}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{Dedicated, life-long learner. Always looking for questions and answers in the data. Known as a highly organized, personable, and resourceful team player. Passionate about the R community.}

\usepackage{booktabs}

% Templates for detailed entries
% Arguments: what when with where why
\usepackage{etoolbox}
\def\detaileditem#1#2#3#4#5{%
\cventry{#1}{#3}{#4}{#2}{\ifx#5\empty\else{\begin{cvitems}#5\end{cvitems}}\fi}\ifx#5\empty{\vspace{-4.0mm}}\else\fi}
\def\detailedsection#1{\begin{cventries}#1\end{cventries}}

% Templates for brief entries
% Arguments: what when with
\def\briefitem#1#2#3{\cvhonor{}{#1}{#3}{#2}}
\def\briefsection#1{\begin{cvhonors}#1\end{cvhonors}}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {October 2020}
    {Ethan Brockmann~~~·~~~Curriculum Vitae}
  {Crafted with \href{https://github.com/mitchelloharawild/vitae}{\{vitae\}}}

%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



data harmonization, data dictionary development and streamline data transfer: Pharmacy rebates

\hypertarget{programming-experience}{%
\section{Programming Experience}\label{programming-experience}}

\begin{itemize}
\item
  3 years using SAS macro language, data steps, and PROC SQL to query large (\textgreater10,000,000 rows) data sets and compile insightful reports for company management
\item
  2 years of experience using R for data science and data visualization, including building static and interactive reports with R Markdown and R Shiny
\item
  Front-end and back-end university classes in C++ and Python in order to obtain a Computer Science minor
\item
  Author and maintainer of the \texttt{edgedata} R package on CRAN
\item
  Familiarity with Git/Github, \LaTeX, HTML, CSS, Javascript, JSON, XML, C, Linux, and Multipass
\end{itemize}

\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\textbf{Actuarial Analyst, R Developer}. BlueCross \& BlueShield of Mississippi. Flowood, MS. June 2017 -- Present

\begin{itemize}
\item
  Go-to analyst for data requests from the CFO and CEO. This often requires custom data visualizations and analysis, and it always requires clear communication of technical concepts.
\item
  Created a complex R Shiny application to track the performance of a predictive model over time. Included an optimized SQL back-end, insightful visualization, and data caching to optimize response time.
\item
  Daily code review given and received. Reviewing for both technical accuracy and business value.
\item
  Author and maintainer of an internal R package to safely interact with the company's database
\item
  Passionate about coding best practices, peer review, and careful version control
\item
  Developed an understanding of many machine learning techniques and their real world applications
\end{itemize}

\textbf{Actuarial Student Intern}. BlueCross BlueShield of Mississippi. Flowood, MS. May 2016 -- August 2016

\begin{itemize}
\item
  Capstone project involved building member risk profiles with ICD-10 diagnosis codes and searching for suspected missing codes
\item
  Built a new predictive model with SQL and Excel to capture undercoding in membership
\end{itemize}

\hypertarget{education}{%
\section{Education}\label{education}}

Bachelor of Science in Mathematics. Minor in Computer Science. Mississippi State University, Starkville, MS. GPA 3.92/4.00. May 2017

\begin{itemize}
\tightlist
\item
  Actuarial exams and other self-study during and after university have given me a solid foundation in statistics and machine learning techniques
\end{itemize}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

Undergraduate Research Project in Graph Theory. Mississippi State University. August 2015-December 2015

\begin{itemize}
\item
  Worked with the independence polynomials of claw free graphs and trees
\item
  Paper available here: \url{https://osebje.famnit.upr.si/~russ.woodroofe/ethan-brockmann.pdf}
\end{itemize}

\end{document}
