%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Ethan Brockmann}{}

\address{740 Hartwood, Brandon, MS 39042}

\mobile{(920) 728-5600}
\email{\href{mailto:ethanbrockmann@gmail.com}{\nolinkurl{ethanbrockmann@gmail.com}}}
\homepage{eeethb.rbind.io}
\github{EeethB}
\twitter{EeethB}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

% Templates for detailed entries
% Arguments: what when with where why
\usepackage{etoolbox}
\def\detaileditem#1#2#3#4#5{%
\cventry{#1}{#3}{#4}{#2}{\ifx#5\empty\else{\begin{cvitems}#5\end{cvitems}}\fi}\ifx#5\empty{\vspace{-4.0mm}}\else\fi}
\def\detailedsection#1{\begin{cventries}#1\end{cventries}}

% Templates for brief entries
% Arguments: what when with
\def\briefitem#1#2#3{\cvhonor{}{#1}{#3}{#2}}
\def\briefsection#1{\begin{cvhonors}#1\end{cvhonors}}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {April 2020}
    {Ethan Brockmann~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{work-experience}{%
\section{Work Experience}\label{work-experience}}

\textbf{Actuarial Analyst}. BlueCross BlueShield of Mississippi.
Flowood, MS. June 2017 -- Present

\begin{itemize}
\item
  Entrusted with leading the R and data science movement at the company
\item
  Became the go-to analyst for data requests from the CFO and CEO
\item
  Created organization's first R Markdown report, first Shiny
  application, and first package
\item
  Achieved this while maintaining core actuarial work such as
  researching data sources and gathering data, verifying data integrity,
  updating actuarial models, and preparing financial, enrollment, and ad
  hoc reports
\end{itemize}

\textbf{Actuarial Student Intern}. BlueCross BlueShield of Mississippi.
Flowood, MS. May 2016 -- August 2016

\begin{itemize}
\item
  Assisted actuarial personnel in core actuarial functions
\item
  Capstone project involved building member risk profiles with diagnosis
  codes and searching for suspected missing codes
\end{itemize}

\textbf{Math Tutor}. Mississippi State University. Starkville, MS.
November 2014 -- December 2015

\begin{itemize}
\item
  Provided additional help to students in historically difficult classes
\item
  Helped one student improve 30\% from test 1 to test 2
\item
  Tutored students in algebra, trigonometry, calculus, linear algebra,
  basic mathematical proof classes, and chemistry
\end{itemize}

\hypertarget{programming-experience}{%
\section{Programming Experience}\label{programming-experience}}

\begin{itemize}
\item
  Author and maintainer of the
  \href{https://github.com/ArctiCondor/edgedata}{\texttt{edgedata}}
  package on Github
\item
  Experience developing R Markdown documents, Shiny applications, and an
  internal organizational R package
\item
  Current position involves updating Excel models with regular VBA
  development
\item
  University classes and data analysis in Python
\item
  Built data structures such as binary trees and linked lists in C++
\item
  Authored research paper and senior seminar papers in \LaTeX
\end{itemize}

\hypertarget{education}{%
\section{Education}\label{education}}

Bachelor of Science in Mathematics. Minor in Computer Science.
Mississippi State University, Starkville, MS. GPA 3.92/4.00. May 2017

Passed actuarial exams P, FM, IFM, SRM, and LTAM

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

Undergraduate Research Project in Graph Theory. Mississippi State
University. August 2015-December 2015

\begin{itemize}
\item
  Worked with the independence polynomials of claw free graphs and trees
\item
  Paper available here:
  \url{https://osebje.famnit.upr.si/~russ.woodroofe/ethan-brockmann.pdf}
\item
  Sage code available here:
  \url{https://osebje.famnit.upr.si/~russ.woodroofe/ethan-brockmann.sage}
\end{itemize}

\end{document}
